A Case Study in Preserving a High Energy Physics Application

### 2014-03-03 paper.tex
content modification: section 6

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}
\subsection{Preservation Integration of Multiple Programs}
The Solution 4 can work well for the preservation and reproduction of one single program. However, different experimenters may execute different analysis programs on the same dataset using the same or overlapping sets of software. Generating one new package for each analysis program from scratch is time-consuming and space-consuming, which makes one data and software preservation mechanism, that can integrate the preservation requirements of different analysis programs, become necessary.

@@

To integrate the data and software from multiple analysis programs into one
package, the concrete information of data and software, such as size, version,
source and the number of files, need to be recorded. we also need to design one
more instructive shell script format, in which the data dependencies and
software dependencies can be clearly expressed and recognized. The packaging
process needs to be re-organized. Packaging utility needs to maintain one list
of current software and data subset already stored in the package. When one
user fork the packaging utility to preserve one program, the
packaging utility will scan the script, get the data and software dependency
part, judge whether each dependency has been inside the package, and only add
the new data and software into the package, and update the package information
and relavant retrieval information.

The architecture of preservation integration of multiple programs is shown in
Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
dependency B, belongs two different programs. Without preservation
integration, B will be preserved twice in the archive, which is
space-consuming. To improve the utilization efficiency of storage resources,
preservation integration of multiple programs is necessary. In the archive,
only one copy of B is stored, which is referred by both scripts and script 2.

@@

Another important factor of data and software preservation is the choice of
preservation granularity. In Solution 4, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

@@

The preservation policy must concern about the size of data. If its size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea. Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable. In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as networked resources is more efficient than preserving it into one package.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, 
direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 4 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

Another solution is to treat the computing environment, software environment
and scientific data as one integral entirety and preserve the entirety
completely. The reproduction of one experiment using this solution is easier.
However, the original machine is not only for one special experiment and may
concern a large amount of software and data unrelevant to the experiment. The
time and space overhead of this solution must be considered.

@@

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, {\tt ls /dirA} is one linux command to list the name of each item under
{\tt /dirA}. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 4. However, when we repeated the command {\tt ls /dirA} using the preserved package, it returned NULL because none of items under it existed in
value of {\tt ls /dirA}, the behavior of the whole program will become incorrect
and unpredictable.

@@

Through this case study, we noticed that the user access module of remote data
and software has a great impact of the preservation mechanism, especially when
we try to integrate the preservation of multiple programs. If all the programs
only refer the original data and software and refuse to modify them, the
preservation is easy and can ignore the data version problem. However, if some
programs try to modify the original data and software to accustom to its own
requirement, the preservation mechanism must provide one way to differentiate
the original data and the special data used in one certain
program. To have a clear understanding of the data access model, more examples
need to be investigated.

@@

At the beginnig of our case study, we generated one package for Matthias's
example based on Solution 4. Several months later, the original machine meets
some problems and the access model of CMSSW was also modified. In this case, if
you want to repeat Matthias's example on the original machine, different 
configurations, including CMSSW\_ARCH, environment variables and CVS access
authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
%here is the new content-hmeng

>>>>

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}
\subsection{Preservation Integration of Multiple Programs}

Different experimenters may execute different analysis
programs on the same dataset using the same or overlapping sets of software.
Generating one new package for each analysis program from scratch is
time-consuming and space-consuming, which makes one data and software
preservation mechanism, that can integrate the preservation requirements of
different analysis programs, become necessary.

@@

To integrate the data and software from multiple analysis programs into one
archive, the concrete information of data and software, such as size, version,
source and the number of files, need to be recorded. 
The packaging
process needs to be re-organized. Packaging utility needs to maintain one list
of current software and data subset already stored in the archive. When one
user utilizes the packaging utility to preserve one program, the
packaging utility scans the script, gets the data and software dependency
part, judges whether each dependency has been inside the package, and only adds
the new data and software into the archive, and updates the package information
and relavant retrieval information.

The architecture of preservation integration of multiple programs is shown in
Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
dependency B, belongs two different programs. Without preservation
integration, B will be preserved twice in the archive. To improve the utilization efficiency of storage resources,
preservation integration of multiple programs is necessary. In the archive,
only one copy of B is stored, which is referred by both scripts.

@@

Another important factor of data and software preservation is the choice of
preservation granularity. In our implementation of Solution 4, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

@@

The preservation policy must concern about the size of data. If data size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea. Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable. In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as networked resources is more efficient than preserving it into one package.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Clear data dependencies is easy to figure
out, but how to figure out implicit data dependencies is complex. The situation
of software dependencies is more complex. The software dependencies include OS,
hardware platform, direct software dependencies and indirect software
dependencies.
The first
three categories are easy to deal with. The acquisition of indirect software
dependencies needs more efforts.

One solution is to treat the computing environment, software environment
and scientific data as one integral entirety and preserve the entirety
completely. The reproduction of one experiment using this solution is easier.
However, the original machine is not only for one special experiment and may
concern a large amount of software and data unrelevant to the experiment. The
time and space overhead of this solution must be considered.

Another solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.

The third solution is to trace the system calls of the experiment execution process
and record the paths of accessed files, which including the files of software dependencies.
Parrot adopts this solution. Even if git is one software dependency, there is no necessary to install git on the new machine.
All the files to guarantee the accurate execution of git has been copied into the package.

@@

Directory is one list of files and subdirectories under it. At first, we only
copy the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, {\tt ls /dirA} is one linux command to list the name of each item under
{\tt /dirA}. Because the directory itself has the name list of items under it, only
the path of the directory is recorded into the namelist in the first phrase of
Solution 4. However, when we repeat the command {\tt ls /dirA} using the preserved package, it returns NULL because none of items under it exists in
the package, the behavior of the whole program will become incorrect
and unpredictable.

@@

The user access module of remote data
and software has a great impact of the preservation mechanism, especially when
we try to integrate the preservation of multiple programs. If all the programs
only refer the original data and software and refuse to modify them, the
preservation is easy and can ignore the data version problem. However, if some
programs try to modify the original data and software to accustom to its own
requirement, the preservation mechanism must provide one way to differentiate
the original data and the special data used in one certain
program. To have a clear understanding of the data access model, more examples
need to be investigated.

@@

At the beginnig of our case study, we generated one package for Matthias's
example based on Solution 4. Several months later, the original machine met
some problems and the access model of CMSSW was also modified. In this case, if
you want to repeat Matthias's example on the original machine, different 
configurations, including CMSSW\_ARCH, environment variables and CVS access
authority need to be modified. However, with the generated package and its map file, we can repeat the experiment directly on the same machine without any modification.
%here is the new content-hmeng
